\documentclass{article}

\usepackage[dvipsnames]{xcolor}
\usepackage {tabularx}
\usepackage{booktabs}
\usepackage {graphicx}

% ================ Title ===============

\title{%
	\vspace{40mm}
	\textbf {
	\Huge {\color[rgb]{0.9,0,0}Blaze} Brigade \\
	\large - Problem Statement -}}

\date{\today}

\author{SFWR ENG 3XA3 - Section L02 \\
	007 (Group 7) \\ \\
	Jeremy Klotz - klotzjj \\
	Asad Mansoor - mansoa2 \\
	Thien Trandinh - trandit \\
	Susan Yuen - yuens2}

% =============== Document ===============

\begin{document}
\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}

%Revision Table
\begin{table}[hp]
    \caption{Revision History} \label{TblRevisionHistory}
    \begin{tabularx}{\textwidth}{llX}
        \toprule
        \textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
        \midrule
        Sept 22, 2016 & All & Created the Development Plan - Rev 0. \\
        Dec 5, 2016 & Asad Mansoor & Added the description of the context in regards to the environment of the software. Derived a clear statement of the problem that needs to be solved - Rev 1. \\
        \bottomrule
    \end{tabularx}
\end{table}

\newpage

%Main Content
Video games emerged in 1972 in the form of Pong, and have since then evolved to become one of the world's most popular forms of entertainment. The video game that we will be refurbishing belongs to a very specific genre: tactical simulation games. Tactical RPGs (role-playing games) first arrived in 1982, and is a descendant of strategy tabletop games, such as chess. The game that we have chosen to refurbish and polish, Tactics Heroes, is largely inspired by a Japanese game series called 'Fire Emblem', which was released in 1990 by Intelligent Systems and Nintendo. Fire Emblem revolutionized the genre by incorporating RPG elements, and as such, the success of the genre in modern day can largely be attributed to this series. \\

Despite being one of the most popular forms of entertainment, games like Fire Emblem have not made their mark on the PC era. The scope of providing such an entertainment should be available to users of various kinds. In that regard, Blaze Brigade would take the very elements that made Fire Emblem a big success and set out to provide a source of entertainment with strategic challenges on a PC. Tactics Heroes with its limited functionality and mild user experience, would be improved into the Blaze Brigade project to further enhance the user experience with new functional features and graphical enhancement that will target users who love the popular genre.\\

In its current state, Tactics Heroes has implemented all of the basic features of a tactical, turn-based combat game. However, the game currently lacks several additional features that could bring the game into a more polished state. Our goal is to re-implement the game while incorporating these elements to provide the user with a more enjoyable gaming experience and a higher level of entertainment. Such an example is the fact that Tactics Heroes requires a minimum of two players to play the game, but our aim is to open up game play to single players as well. This allows for more frequent gameplay and entertainment for its users as it takes away the requirement of having a second player to play against. \\

The stakeholders of the project include its users, its own developers, and the original developers of Tactics Heroes. Blaze Brigade will serve as a means of entertainment for its developers and its users. The game's implementation can also serve as a guideline for Tactics Heroes' original developers to further improve their game by incorporating our project's features, as well as modern software development tools and concepts.\\

To the extent of its environment, Blaze Brigade would be played on a desktop or laptop computer running Windows OS, to immerse users in a fun and enriching source of entertainment. The type of users could vary from age, gender and even gaming experience. As long as the user has a Windows machine and has access to the Game Executable and folder, the game could potentially be played anywhere as long as it is equipped with a pointing device (ie. mouse or touchpad). This is an ideal situation for a home setting or during break-hours at work.

\end{document}